\newcommand{\blank}{\rule[-0.1pt]{15pt}{0.5pt}\ }

\begin{PuzzleClues}{

    \textbf{Across}}\\
    \Clue{2}{HOLYHANDOFF}{Statue at 5 Across of Mary and Joseph using
      baby Jesus as a football on First and 10?}\\
    \Clue{5}{NOTREDAME}{Allison's alma mater}\\
    \Clue{6}{CAKE}{Standard wedding dessert}\\
    \Clue{8}{TENNIS}{Racquet sport, and a husband-and-wife band we saw
      at 9:30 Club with the Groom's sister}\\
    \Clue{9}{JOHNPAULJONES}{Permanent resident of the Naval Academy crypt}\\
    \Clue{12}{GROOM}{Jeff, today}\\
    \Clue{13}{FIRSTDOWNMOSES}{Old Testament prophet signaling a successful fourth-down sneak at 5 Across?}\\
    \Clue{18}{BRIDE}{Allison, today}\\
    \Clue{19}{ZOLTARSPEAKS}{As made famous in \textit{Big}, we saw
      this fortune-telling arcade game on our unofficial first date}\\
    \Clue{21}{HYDEPARK}{London green spot perfect for strolling, or
      polemicizing at 32 Down}\\
    \Clue{22}{BORROWED}{Something \blank (1 of 4)}\\
    \Clue{23}{TWILIGHTSTRUGGLE}{Cold War-themed game, named after a Kennedy coinage, that has occupied many of Jeff's and Allison's weekends}\\
    \Clue{27}{MILO}{The Best Dog}\\
    \Clue{28}{MIDDLEBURY}{Jeff's alma mater}\\
    \Clue{30}{BAND}{One is on the stage, or on the third finger}\\
    \Clue{31}{KISS}{You may \blank the bride}\\
    \Clue{33}{DOMINION}{Deck-building game popular amongst several guests; also a Virginia brewery that makes good root beer and okay beer}\\
    \Clue{34}{TOSS}{The bride does this with 57 Across}\\
    \Clue{35}{ITALY}{Honeymoon destination}\\
    \Clue{36}{MAXS}{Jeff associates this possessive with a Baltimore
      sports bar with 100+ taps; Allison with the Grinch's dog}\\
    \Clue{39}{CHERRY}{Fruit component of 20 Down}\\
    \Clue{41}{BLUSH}{Bride's do this}\\
    \Clue{42}{RIGHTPROPER}{This DC brewery's name sounds British,
      but with half its fermenters dedicated to Brett, its beer is
      American and Belgian}\\
    \Clue{43}{BLUE}{Something \blank (1 of 4)}\\
    \Clue{44}{ADIRONDACKCHAIR}{Seat of choice at 28 Across.  There are
    a few on the deck here}\\
    \Clue{46}{MRS}{Bride's new title}\\
    \Clue{48}{NEW}{Something \blank (1 of 4)}\\
    \Clue{49}{VIN}{With 909, this Annapolis wine bar witnessed our first date and engagement}\\
    \Clue{55}{IDO}{What's my line?}\\
    \Clue{56}{VANMORRISON}{Artist who recorded our first dance song and many more played tonight}\\
    \Clue{57}{BOUQUET}{Floral arrangement carried by the bride}\\
    \Clue{58}{THREEFLOYDS}{Munster heavy metal brewery who worships the Dark Lord}\\
    \Clue{60}{BOH}{With "Nattie", B'more's favorite cheap brew}\\
    \Clue{61}{TOASTS}{Good ones have something funny, something sweet, and end with everyone drinking}\\
    \Clue{62}{AISLE}{The bride walks down it}\\
    \Clue{63}{TAN}{Some people get one on their honeymoon}\\
    \Clue{64}{BOWTIE}{One is around the groom's neck}\\
    \Clue{65}{RING}{Relax, Beyonce: Jeff did put this on it}\\
    \end{PuzzleClues}
    \begin{PuzzleClues}{\textbf{Down}}\\  
    \Clue{1}{CHAMP}{Friendly monster lurking off Burlington}\\
    \Clue{3}{ONE}{Two become \blank}\\
    \Clue{4}{DANCINGGNOME}{Pittsburgh brewery named after carousing garden dwellers?}\\
    \Clue{5}{NOONIESDELI}{Jeff ate a lot of sandwiches at this deli in college}\\
    \Clue{7}{BACHELORFARMER}{Minneapolis nordic eatery (two words): second grows crops, first no longer describes Jeff}\\
    \Clue{10}{SCORPIO}{Allison's sign; also a Simpsons guest villian}\\
    \Clue{11}{PISCES}{Jeff's sign; some guests are eating this tonight}\\
    \Clue{14}{OLD}{Something \blank (1 of 4)}\\
    \Clue{15}{TOUCHDOWNJESUS}{Famous mural of Christ signaling the breaking of the plane?}\\
    \Clue{16}{DIAMOND}{A girl's best friend}\\
    \Clue{17}{PURPLESPLEASURE}{Erotically named offering from 5 Down}\\
    \Clue{19}{ZULU}{Our wedding was at 1700 in this time zone.
      (I know, this is filler...)}\\
    \Clue{20}{SPOONBRIDGE}{With 39 Across, Minneapolis sculptural landmark.  Despite the name, you can't walk on it}\\
    \Clue{22}{BIND}{The ties that \blank}\\
    \Clue{24}{LCDSOUNDSYSTEM}{\textit{Losing My Edge} artist, and one of the
      first acts to play at The Anthem.  We saw them with 8000
      middle-aged hipsters.}\\
    \Clue{25}{HAMILTON}{Allison left Jeff \textit{Helpless} with tickets to
      this smash musical on Broadway}\\
    \Clue{26}{GRANDFATHERMOUNTAIN}{North Carolina hiking spot named for a family patriarch with a very technical climb (by Appalachian standards)}\\
    \Clue{29}{DAD}{He gives her away}\\
    \Clue{32}{SPEAKERSCORNER}{Get on your soapbox here in 21 Across}\\
    \Clue{37}{CHESAPEAKEBAY}{DelMarVa's favorite body of water}\\
    \Clue{38}{MR}{Groom's title}\\
    \Clue{40}{YES}{That's what she said}\\
    \Clue{45}{ROSE}{Would this by any other name smell as sweet?}\\
    \Clue{47}{SAINTMARYS}{Our ceremony venue}\\
    \Clue{50}{CHVRCHES}{Misspelled band named for ceremony venues?}\\
    \Clue{51}{BURLEYOAK}{Eastern Shore bewery named for a tree and known
      for fruited sours}\\
    \Clue{52}{WHITE}{Color of the bride's dress}\\
    \Clue{53}{JOSHRITTER}{Our favorite musician, whenever he's touring
      we're \textit{Gettin' Ready to Get Down}}\\
    \Clue{54}{LOVELETTER}{Amorous missive; also a card game that's our
    gift to you!}\\
    \Clue{58}{TINGTINGS}{With "The", this UK guy-girl duo was the first concert we saw together.  We were not at \textit{The Wrong Club}}\\
    \Clue{59}{SUPERIOR}{Great Lake we waded in from Duluth.  Brrr!}\\

        \textbf{Unless you've been stalking us for the past 4 years, this
    crossword puzzle will be HARD.  If you get stuck, try
    asking your fellow guests, who may know us in different ways.
    If you get really stuck, Google can help on many of the clues, and
    the solution is printed on the back.  Have fun!}
        
\end{PuzzleClues}
